Viscous Transport in Eroding Porous Media

### 2019-05-16 docs/transport/erosion_transport.tex
do the result section in transport paper

Furthermore, how long the body lasts for depends on not only the size of the body 
but also the location of the body. 
For example, the first three vanishing bodies are 
body 12 (as t=0.0256), 4 (as t=0.0278), then 17 (as t=0.0287). 
Since body 4 is located in the main flow channel so 
the body 4 is vanished earlier than body 17 
even the initial size of body 4 is larger than the size of body 17.
This channel will keep expanding and the bodies around this channel will vanish earlier than others. 
After body 17, the next 8 vanished bodies with respect to time are body 19 (as t=0.0312),  
 body 7 (as t=0.0325), body 20 (as t=0.0329), body 8 (as t=0.0349), body 10 (as t=0.0353),
 body 3 (as t=0.0356), body 14 (as t=0.0363), then body 9 (as t=0.0376).  
All of these eight bodies were around this channel.

>>>>

Furthermore, how long the body lasts for depends on not only the size of the body 
but also the location of the body. 
For example, the first three vanishing bodies are 
body 12 (as t=0.0256), 4 (as t=0.0278), then 17 (as t=0.0287). 
Since body 4 is located in the main flow channel so 
the body 4 is vanished earlier than body 17 
although the initial size of body 4 is larger than the size of body 17.
This channel will keep expanding and the bodies around this channel will vanish earlier than others. 
After body 17, the next 8 vanished bodies with respect to time are body 19 (as t=0.0312),  
 body 7 (as t=0.0325), body 20 (as t=0.0329), body 8 (as t=0.0349), body 10 (as t=0.0353),
 body 3 (as t=0.0356), body 14 (as t=0.0363), then body 9 (as t=0.0376).  
All of these eight bodies were around this channel before they are gone.
